%------------------------------------------------

\section{Discrete Probability}\index{Discrete Probability}

Your friend (not as diligent as you) did not study for his American History test. It's multiple choice, so he knows he has a chance to get each answer correct by simply guessing. There are 25 questions with 4 answer choices each, how likely is it that your friend passes the test? There is .000043 chance that your friend scores a 60\% or higher! His hope is misplaced!

\noindent Probability is the mathematical tool used to calculate the likelihood of an event, and we find probability either through counting or measuring area. Probability questions handled by counting are called discrete probability questions.

\subsection{Flipping Some Coins}

\begin{example}\label{flipcoins}
For example, what is probability of flipping two heads in two coin flips? 

\noindent \textbf{Solution:} First, we need to count the ways we can flip two coins. This set of all possibilities is called the \textbf{universal set}.


\begin{equation}
    S = \{TT, TH, HT, HH\}
\end{equation}

\noindent Next we find the ways our event is satisfied. This set is called the \textbf{event set}.

\begin{equation}
A = \{HH\}    
\end{equation}

\noindent Since out of the four possible options, only one satisfied what we want, we say that the probability we want is $P(A) = |A| / |S| = 1/4$.
\end{example}

\noindent Example \ref{flipcoins} illustrates how to calculate probability.

\begin{definition}
Let $A$ be a subset of a universal set $U$. Then the probability of $A$ is $P(A) = |A|/|S|$.
\end{definition}

\noindent Let's practice this idea.

\begin{exercise}
What is the probability of flipping exactly one head in two coin flips?
\end{exercise}

\vspace{1in}

\begin{exercise}
What is the probability of flipping one head in three coin flips? (Find the universal and event sets.)
\end{exercise}

\vspace{1.5in}

\subsection{Die Rolls}
We will look at a new context, but the same ideas apply.

\begin{exercise}
What is the probability of rolling an odd number when rolling a six-sided die?
\end{exercise}

\vspace{1.5in}

\begin{exercise}
What is the probability of rolling a sum of 7 when rolling two six-sided die?
\end{exercise}

\vspace{1.5in}