%------------------------------------------------

\section{HOMEWORK: The Fibonacci Sequence}\index{HOMEWORK: The Fibonacci Sequence}

The Fibonacci Numbers are defined as follows:
\begin{equation}
    F_1=1, F_2 = 1, \text{ and } F_n=F_{n-1}+F_{n-2}, \text{ for } n \geq 3.
\end{equation}
\noindent So then the Fibonacci Sequence can be listed as 1, 1, 2, 3, 5, $\ldots$ 

\noindent The Fibonacci Sequence is one of the most famous applications of mathematics you can find. We find examples of this curious sequence everywhere from plants to architecture and from music to human anatomy. We will explore a little about the Fibonacci Sequence now.

\begin{exercise}
Write out the first 15 Fibonacci numbers.
\end{exercise}	

\vspace{3in}



\subsection{The Golden Rectangle and Golden Spiral}

In addition to interesting number formulas, the Fibonacci sequence leads to something called the Golden Rectangle. 

\begin{exercise}
Use, as a reference, the article “Patterns in Natures: Where to Spot Spirals” \cite{patterns_in_nature} to construct the Golden Rectangle and the Golden Spiral below:
\end{exercise} 
\footnotesize{https://www.scienceworld.ca/stories/patterns-nature-where-spot-spirals/}

\vspace{3in}

\begin{exercise}
There are many applications of the Fibonacci Sequence! Look online to find 10 places you can find the Fibonacci sequence. Be sure to include the golden rectangle, the golden spiral, nature, and art in your list.
\end{exercise}

\begin{enumerate}
    \item 
    \item
    \item
    \item
    \item
    \item
    \item
    \item
    \item
    \item
\end{enumerate}
