%------------------------------------------------

\section{HOMEWORK: Terrance Tao and the Fields Medal}\index{HOMEWORK: Terrance Tao and the Fields Medal}

There is no Nobel Prize in mathematics unfortunately. However, there is the much more prestigious Fields Medal given to outstanding mathematicians no older than 40 once every four years, awarded by the International Mathematics Union (IMU) \cite{IMU},

\subsection{Who has Won the Fields Medal?} 

\begin{exercise}
Research a person who won the Fields Medal (other than Terence Tao). Who are they? Where are they from? And for what reason did the earn the Fields Medal?
\end{exercise}

\blanks
\blanks

\subsection{Terrance Tao}

Terence Tao is one of the Fields Medal recipients, and he may be the greatest mathematician of our time. The Sydney Morning Herald discussed Tao's success.

\begin{exercise}
Read ``Terence Tao: the Mozart of Maths by The Sydney Morning Herald" \cite{tao}.
\end{exercise}
{\footnotesize https://www.smh.com.au/lifestyle/terence-tao-the-mozart-of-maths-20150216-13fwcv.html}

\begin{exercise}
Tao seems to be in a tier of his own in the mathematics world. List three aspects of Tao that seem to mesmerize mathematicians of the world.
\end{exercise}

\begin{enumerate}
    \item \hspace{1.5in} Source: \\
    \item \hspace{1.5in} Source: \\
    \item \hspace{1.5in} Source: 
\end{enumerate}

\begin{exercise}
Visit Tao’s Wikipedia page, and list one of his notable awards other than the Fields medal.
\end{exercise}

\blanks

