%------------------------------------------------

\section{HOMEWORK: Mind-Boggling Math Facts}\index{HOMEWORK: Mind-Boggling Math Facts}

From the dawn of human history, people have turned to mathematics for answers to a variety complicated problems. Mathematics has been to found to provide the logic and sound consistency needed to approach the world empirically. Studying mathematics have brought significant advances in everything from Chemistry to Psychology to Economics to Engineering. 

But sometimes math has pointed us in surprising direction. Sometimes, we find things that hard to believe.

\subsection{Live Science and 5 Mind-Boggling Math Facts (Homework)} 

Live Science (livescience.com) has numerous interesting science and mathematics articles. 

\begin{exercise} 
Read the article from Live Science entitled ``5 Mind-Boggling Math Facts" \cite{livescience}.
\end{exercise}
{\footnotesize https://www.livescience.com/26584-5-mind-boggling-math-facts.html. You can locate the video for Sphere Inversion can be found here: https://youtu.be/iynrV-3I9CY \cite{sphere}.}

\vspace{.5cm}

\begin{exercise}
Have you heard of any of these facts before? Do any of these facts seem hard to believe at first glance?
\end{exercise}

\blanks
\blanks

\vspace{.5cm}

\begin{exercise}
Which fact did you find to be the most ``mind-boggling"? Explain your reasoning.
\end{exercise}

\blanks
\blanks

\subsection{More Interesting Facts} 

\begin{exercise}
Locate the Canvas discussion post "More Interesting Facts" and share a resource pointing to another ``mind-boggling" math fact.
\end{exercise}








